Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}

### 2024-07-17 src/tex/ms.tex
[showyourwork] overleaf sync

\textcolor{red}{Q: Do we want to put an observing log in the appendix?}

\subsection{UVES observations}

To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
%
The details for these observations are given in \cite{vansluijs2019}, and summarised here.
%
These observations were all obtained using the same instrument setup.
%
We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
%
In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA to $\sim 5000$ \AA in the blue arm, and $\sim 5650$ \AA to $\sim 9560$ \AA in the red arm.
%
For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
%
For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).

@@

\subsection{Initial data processing}
Starting from the 2d spectra, the data from both instruments was processed in similar ways.
%
Each order was treated separately, with the main focus on orders \textcolor{red}{NN, MM and OO} for HARPS and \textcolor{red}{NN, MM, OO} for UVES as those orders contain the main CN bandhead as well as the Ca II H \& K lines, which are used to identify the exocomets.
%
All the spectra were transformed into the stellar rest-frame and onto a common wavelength grid using linear interpolation.

@@

\subsubsection{Combining the spectra}
After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits. This could potentially re
 For all the night spectra:

 We median combine all the nights together.

 Bin the spectrum and clip it, interpolate using a cubic spline.

 Divide this interpolated cubic spline into each of the nightly spectra.

THis removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.

@@

\subsection{Other Species? CO$^+$, C$_2$?}

>>>>

\textcolor{red}{Q: Do we want to put an observing log in the appendix?}
\textcolor{red}{Q: Do we want to attempt to use the S1D, as they may have less issues with wiggles if the blaze profile was removed.}
\subsection{UVES observations}

To supplement the HARPS observations, we use 160 epochs of \ac{uves} observations obtained between 01 April, 2017 and April 18, 2018 under programme 599.C-0751.
%
The details for these observations are given in \cite{vansluijs2019}, and summarised here.
%
These observations were all obtained using the same instrument setup.
%
We used the standard 437+760 mode of \ac{uves}, which uses the \#2 dichroic to allow simultaneous observations in both the red and blue arm.
%
In this mode, the CD\#2 and CD\#4 cross-dispersers are used in the blue and red-arm, respectively, providing a simultaneous wavelength coverage of $\sim 3730$ \AA{} to $\sim 5000$ \AA{} in the blue arm, and $\sim 5650$ \AA{} to $\sim 9560$ \AA{} in the red arm.
%
For the remainder of the paper, we will only focus on the data from the blue arm of \ac{uves}, as this covers the strong \ce{CN} (0-0) band-head seen in Solar system comets.
%
For the blue arm, a 0.3''-wide slit was used to obtain the highest possible resolving power ($\sim$90,000 before an intervention on the instrument in October 2017, and $\sim$100,000 after the intervention).

@@

\subsection{Initial data processing}
Starting from the 2d spectra, the data from both instruments was processed in similar ways.
%
Each order was treated separately, with the main focus on orders \textcolor{red}{NN, MM and OO} for HARPS and \textcolor{red}{NN, MM, OO} for UVES as those orders contain the main CN bandhead as well as the \ion{Ca}{ii} H \& K lines, which are used to identify the exocomets.
%
All the spectra were transformed into the stellar rest-frame and onto a common wavelength grid using linear interpolation.

@@

\subsubsection{Combining the spectra}
After the blaze-variation corrections, all the spectra within a night are combined in order to further boost the signal-to-noise and improve the detection limits.

For the spectra within a given night:

\begin{itemize}
\item We median combine all the nights together.

\item Bin the spectrum and clip it, interpolate using a cubic spline.

\item Divide this interpolated cubic spline into each of the nightly spectra.

\end{itemize}

This removes the blaze function, but there remain low spatial frequency variations between different nights, due to the changing slit illumination as the star moves across the spit aperture.

@@

%\subsection{Other Species? CO$^+$, C$_2$?}
